A Modular Handwritten Kanji Recognition Schema

### 2014-10-05 doc/tacs2014/article.tex
Final revision based on reviewer feedback

	\begin{abstract}
		Handwriting continues to play a significant role in daily life, warranting continued research in the field of intelligent character recognition.
		%Due to their vast number of symbols, east asian scripts such as Japanese remain challenging to process efficiently with high accuracy.
		East asian scripts, such as Japanese, remain challenging to process efficiently with high accuracy due to their vast number of symbols.
		In this work, a modular design schema based on reviews of previous work and the characteristics of the Japanese kanji sinographs is presented, along with
		the description of an ongoing effort to implement and evaluate a handwriting recognition system that incorporates online feature extraction,
		category clustering, and artificial neural networks.

	\end{abstract}
	\medskip
	\begin{IEEEkeywords}
		Intelligent character recognition, handwriting recognition, kanji recognition, artificial neural network.
	\end{IEEEkeywords}

@@

	Although a variety of efficient digital input methods have become all but second nature to recent generations, for the vast majority
	handwriting remains an integral activity in daily life.
	The importance to further improve upon the state-of-the-art in handwriting recognition is underlined not only by the continued prevalence of 
	handwriting, but also by the need to digitalize archived material, its significant role in the development of fine motor skills,
	and a variety of other areas of application, such as signature verification. \cite{plamondon2000online}

	As an area of research, handwriting recognition predates even the digital computer. In 1888, Elisha Gray was awarded a patent %\cite{gray1888telautograph}
	for the Telautograph, which is considered a precursor to the stylus and digitizer, and in
	a 1957 publication, T. L. Dimond summarized early character recognition efforts and introduced the Stylator, an early input recognition device. \cite{dimond1957devices}

	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms, with noteworthy successful techniques
	currently in widespread use including support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty, tappert1990state}

@@

	The Japanese writing system consists of the two \emph{kana} syllabaries \emph{hiragana} and \emph{katakana},
	as well as the sinographs commonly known as \emph{kanji}---literally ``Han characters''---that stem from China.
	The Japanese Ministry of Education's \mbox{official} ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
	baseline characters taught in elementary and secondary education. \cite{hadamitzky2012japanese}
	This set is far from exhaustive, though: the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.

	Although the characters are vast in number and differ significantly from one another in terms of complexity (see figures \ref{fig_kanji_sample}
	and \ref{fig_kanji_stroke_hist}), the writing system itself is not arbitrary. Any kanji may be broken down into smaller units, known as graphemes, 
	and they are commonly ``classified'' by basic, frequently occurring components referred to as radicals.
	Furthermore, stroke order is dictated by a set of rules. In essence, kanji are written from top to bottom and left to right within imagined squares. \cite{foerster1994kanji}

	These properties are often leveraged in kanji recognition systems, but not without penalty: relying on the correct stroke order during online
	recognition, for instance, severely impacts recognition rates when a user provides erroneous input---even though it may still be \emph{visually} correct. \cite{shin2002optimal}

	While certain aspects such as noise reduction and normalization remain similar across systems, the characteristics mentioned above result in
	recognition systems designed for western input not performing satisfactorily when applied to east asian script \cite{jager2003state, tappert1990state}%, liu2004online}
	---unless the solution relies on complex techniques such as  ``deep'' neural networks. \cite{ciresan2012multi}

@@

	\begin{figure}
		\centering
		\begin{tikzpicture}[font=\small]
			\begin{axis}[
				ycomb,
				xlabel={Number of Strokes},
				ylabel={Number of Characters},
			]
				%\addplot[fill=white] coordinates {
				\addplot [] coordinates {
					(1, 6)
					(2, 32)
					(3, 64)
					(4, 115)
					(5, 151)
					(6, 199)
					(7, 318)
					(8, 434)
					(9, 473)
					(10, 544)
					(11, 581)
					(12, 581)
					(13, 532)
					(14, 435)
					(15, 434)
					(16, 369)
					(17, 299)
					(18, 207)
					(19, 175)
					(20, 135)
					(21, 106)
					(22, 69)
					(23, 49)
					(24, 37)
					(25, 20)
					(26, 12)
					(27, 8)
					(28, 6)
					(29, 3)
					(30, 2)
				};
			\end{axis}
		\end{tikzpicture}
		\caption{Distribution of 6,400 kanji by stroke count. \emph{Source: KanjiVG.} \cite{kanjivg}}
		\label{fig_kanji_stroke_hist}
	\end{figure}

@@

	After structuring the search space by clustering, Yang et al. perform two-stepped offline recognition by first
	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
	whose centroid most closely matched the input. \cite{yang2003accelerating}

	In \emph{Hybrid Pen-Input Character Recognition System Based on Integration of Online-Offline Recognition},
	the authors present a system that leverages the advantages provided by each type of recognition.
	In addition to a discussion of various integration techniques, two feature extraction methods are described in detail: 
	a gradient-based technique for offline input, and a recursive substroke extractor for online input. \cite{tanaka1999hybrid}

@@

	\emph{Online Handwritten Kanji Recognition Based on Inter-Stroke Grammar} explains the hierarchical structure of kanji,
	and explores how to leverage this information using stochastic context-free grammars. \cite{ota2007online}

	Finally, \emph{Best Practices for Convolutional Neural Networks Applied to Visual Document Analysis} by Simard, et al. underlines the
	potential of convolutional neural networks and provides a variety of techniques and guidelines directly applicable to the development of a fine-grain classifier. \cite{simard2003best}

@@

	Improving the input data, especially by making it more uniform with respect to available training data, has the potential
	to greatly increase recognition rates. In the case of offline input, techniques include noise reduction,
	cropping, and scaling; for online input, strokes may be analyzed and altered on-the-fly to increase consistency.
	Other possibilities include blurring or otherwise distorting input data in order to generalize it. \cite{razzak2009combining}

@@

	K-means clustering is often employed for this type of segmentation task, as is the LGB algorithm. \cite{yang2003accelerating}
	%It is worth mentioning that optimally allocating $n$ elements in $k$ partitions is an NP-hard problem, even in the case of $k = 2$. \cite{drineas2004clustering}

@@

	Acting upon the vector provided by the feature extractor, the router---or coarse classifier---should indicate
	within which partition the category corresponding to the input is most likely located. This component could
	be contrived to indicate not only one but multiple targets in order to dampen the effect of erroneous routing.

	A 2014 publication by Zhu and Nakagawa documents the use of genetic algorithms to programmatically generate robust coarse classifiers. \cite{zhu2014robust}

@@

	\section{Experiments \& preliminary results}
	\label{sec:experiments}

	An online kanji recognition system based on the design schema outlined in the previous section is
	currently being implemented. This system will be evaluated on established testing benchmarks
	as well as in the form of a mobile application. The diagram in figure \ref{fig_experimental_implementation} 
	explains how the components interact.

@@

	With the intent of progressively improving the various facets of the system,
	the first feature extractor was made as straightforward as possible: each stroke is directly
	classified with a letter as illustrated in figure \ref{fig_stroke_categories} based solely
	on its start and endpoints. Table \ref{tbl_stroke_analysis} contains a summary of the
	result of classifying the 6,400 elements in the KanjiVG dataset in this manner.
	%We speculate that excluding pen-up motions will result in a more error-resilient system.
	Intuitively, excluding pen-up motions should result in a more error-resilient system, due to
	the correct order of the strokes not being taken into account.

@@

	Equipped with their respective feature vectors, the 6,400 categories were partitioned into 50
	mutually exclusive clusters using the K-means++ algorithm. \cite{arthur2007k}
	Based on the information provided
	in table \ref{tbl_stroke_analysis}, only the five dimensions A, B, F, G, and H were utilized as sorting parameters.
	The number of clusters was determined empirically, using Mardia's rule of thumb \mbox{$k \approx \sqrt{n / 2}$} \cite{mardia2005multivariate}
	as an upper limit.

	%\begin{table}
	%	\renewcommand{\arraystretch}{1.3}
	%	\caption{Some form of cluster sample}
	%	\label{tbl_sample_clusters}
	%	\centering
	%	\begin{tabular}{c}
	%		We could list centroid info and some sample kanji. \\
	%		But not \emph{all} the clusters\ldots TMI. \\
	%	\end{tabular}
	%\end{table}

@@

	Initially, three simple routing strategies are being applied: a lookup table, a function that
	identifies the most similar centroid, and a feedforward neural network. One auxiliary goal
	at this stage---in particular with the ANN---is creating some degree of resilience to errors
	such as a missing or incorrectly traced strokes.

@@

	%We are currently designing and evaluating convolutional neural networks to perform final, visual comparisons.
	Current efforts are focused on designing and evaluating convolutional neural networks to perform final, visual comparisons.
	\mbox{Convolutional} neural networks are known to provide a measure of resilience against translation and rotation,
	thus lending themselves well to the task of offline character recognition.

	As previously stated, the comparatively small set of candidates (in current experiments averaging 128 kanji)
	implies that each cluster model requires a lower degree of complexity. It may also be expected that---seeing
	how each partition is likely to contain many similar-looking characters---the networks will be more likely
	to correctly discern between more minute differences that might have been generalized away in a larger-scale network.

	Finally, by focusing solely on offline recognition at this stage, a significantly larger body of training data
	---such as the ETL character database, which contains hundreds of thousands of handwritten kanji samples \cite{yamamoto1986recognition}---may be utilized.

@@

	The experiments documented in this paper are an initial \mbox{attempt} at implementing a kanji handwriting recognition \mbox{system}
	based on the outlined design methodology---numerous venues still remain to be explored.

>>>>

	\begin{abstract}
		Handwriting continues to play a significant role in daily life, warranting continued research in the field of intelligent character recognition.
		East asian scripts, such as Japanese, remain challenging to process efficiently with high accuracy due to their vast number of symbols.
		In this work, a modular design schema based on reviews of previous work and the characteristics of the Japanese kanji sinographs is presented, along with
		the description of an ongoing effort to implement and evaluate a handwriting recognition system that incorporates online feature extraction,
		category clustering, and artificial neural networks.
	\end{abstract}

	\medskip
	\begin{IEEEkeywords}
		Intelligent character recognition, handwriting recognition, kanji recognition, artificial neural network.
	\end{IEEEkeywords}

@@

	Although a variety of efficient digital input methods have become all but second nature to recent generations, for the vast majority
	handwriting remains an integral activity in daily life.
	The importance to further improve upon the state-of-the-art in handwriting recognition is underlined not only by the continued prevalence of 
	handwriting, but also by the need to digitalize archived material, its significant role in the development of fine motor skills,
	and a variety of other areas of application, such as signature verification \cite{plamondon2000online}.

	As an area of research, handwriting recognition predates even the digital computer. In 1888, Elisha Gray was awarded a patent %\cite{gray1888telautograph}
	for the Telautograph, which is considered a precursor to the stylus and digitizer, and in
	a 1957 publication, T. L. Dimond summarized early character recognition efforts and introduced the Stylator, an early input recognition device \cite{dimond1957devices}.

	The decades of research since has introduced a vast number of recognition methods for writing in any and all forms, with noteworthy successful techniques
	currently in widespread use including support vector machines, hidden Markov models, and artificial neural networks \cite{fujisawa2008forty, tappert1990state}.

@@

	The Japanese writing system consists of the two \emph{kana} syllabaries \emph{hiragana} and \emph{katakana},
	as well as the sinographs commonly known as \emph{kanji}---literally ``Han characters''---that stem from China.
	The Japanese Ministry of Education's \mbox{official} ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
	baseline characters taught in elementary and secondary education \cite{hadamitzky2012japanese}.
	This set is far from exhaustive, though: the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.

	Although the characters are vast in number and differ significantly from one another in terms of complexity (see figures \ref{fig_kanji_sample}
	and \ref{fig_kanji_stroke_hist}), the writing system itself is not arbitrary. Any kanji may be broken down into smaller units, known as graphemes, 
	and they are commonly classified by basic, frequently occurring components referred to as radicals.
	Furthermore, stroke order is dictated by a set of rules. In essence, kanji are written from top to bottom and left to right within imaginary squares \cite{foerster1994kanji}.

	These properties are often leveraged in kanji recognition systems, but not without penalty: relying on the correct stroke order during online
	recognition, for instance, severely impacts recognition rates when a user provides erroneous input---even though it may still appear to be \emph{visually} correct \cite{shin2002optimal}.

	While certain aspects such as noise reduction and normalization strategies remain similar across systems, the aforementioned characteristics result in
	recognition systems designed for western input not performing satisfactorily when applied to east asian script \cite{jager2003state, tappert1990state}%, liu2004online}
	---unless the solution relies on complex techniques such as  ``deep'' neural networks \cite{ciresan2012multi}.

@@

	\begin{figure}
		\centering
		\begin{tikzpicture}[font=\small]
			\begin{axis}[
				ycomb,
				xlabel={Number of Strokes},
				ylabel={Number of Characters},
			]
				%\addplot[fill=white] coordinates {
				\addplot [] coordinates {
					(1, 6)
					(2, 32)
					(3, 64)
					(4, 115)
					(5, 151)
					(6, 199)
					(7, 318)
					(8, 434)
					(9, 473)
					(10, 544)
					(11, 581)
					(12, 581)
					(13, 532)
					(14, 435)
					(15, 434)
					(16, 369)
					(17, 299)
					(18, 207)
					(19, 175)
					(20, 135)
					(21, 106)
					(22, 69)
					(23, 49)
					(24, 37)
					(25, 20)
					(26, 12)
					(27, 8)
					(28, 6)
					(29, 3)
					(30, 2)
				};
			\end{axis}
		\end{tikzpicture}
		\caption{Distribution of 6,400 kanji by stroke count. \emph{Source: KanjiVG} \cite{kanjivg}.}
		\label{fig_kanji_stroke_hist}
	\end{figure}

@@

	After structuring the search space by clustering, Yang et al. perform two-stepped offline recognition by first
	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
	whose centroid most closely matched the input \cite{yang2003accelerating}.

	In \emph{Hybrid Pen-Input Character Recognition System Based on Integration of Online-Offline Recognition},
	the authors present a system that leverages the advantages provided by each type of recognition.
	In addition to a discussion of various integration techniques, two feature extraction methods are described in detail: 
	a gradient-based technique for offline input, and a recursive substroke extractor for online input \cite{tanaka1999hybrid}.

@@

	\emph{Online Handwritten Kanji Recognition Based on Inter-Stroke Grammar} explains the hierarchical structure of kanji,
	and explores how to leverage this information using stochastic context-free grammars \cite{ota2007online}.

	Finally, \emph{Best Practices for Convolutional Neural Networks Applied to Visual Document Analysis} by Simard, et al. outlines the
	potential of convolutional neural networks and provides a variety of techniques and guidelines directly applicable to the development of a fine-grain classifier \cite{simard2003best}.

@@

	Improving the input data, especially by making it more uniform with respect to available training data, has the potential
	to greatly increase recognition rates. In the case of offline input, techniques include noise reduction,
	cropping, and scaling; for online input, strokes may be analyzed and altered on-the-fly to increase consistency.
	Other possibilities include blurring or otherwise distorting input data in order to generalize it \cite{razzak2009combining}.

@@

	K-means clustering is often employed for this type of segmentation task, as is the Linde-Buzo-Gray algorithm.% \cite{yang2003accelerating}.
	%It is worth mentioning that optimally allocating $n$ elements in $k$ partitions is an NP-hard problem, even in the case of $k = 2$. \cite{drineas2004clustering}

@@

	Acting upon the vector provided by the feature extractor, the router---or coarse classifier---should indicate
	within which partition the category corresponding to the input is most likely located. his component could
	be contrived to indicate not only one but multiple targets in order to dampen the effect of erroneous routing.

	A 2014 publication by Zhu and Nakagawa documents the use of genetic algorithms to programmatically generate robust coarse classifiers \cite{zhu2014robust}.

@@

	%\section{Experiments \& preliminary results}
	\section{Experimental design \& preliminary results}
	\label{sec:experiments}

	An online kanji recognition system based on the design schema outlined in the previous section is
	currently being implemented. This system will be evaluated on established testing benchmarks
	as well as in the form of a mobile application. The diagram presented in figure \ref{fig_experimental_implementation} 
	explains how the various components interact.

@@

	With the intent of progressively improving the various facets of the system,
	the first feature extractor was made as straightforward as possible: each stroke is directly
	classified with a letter, as illustrated in figure \ref{fig_stroke_categories}, based solely
	on its start and endpoints. Table \ref{tbl_stroke_analysis} presents a statistical overview of the
	result of classifying the 6,400 elements in the KanjiVG dataset in this manner.
	Intuitively, excluding pen-up motions should result in a more error-resilient system, due to
	the \emph{correct order} of the strokes not being taken into account.

@@

	Equipped with their respective feature vectors, the 6,400 categories were partitioned into 50
	mutually exclusive clusters using the K-means++ algorithm \cite{arthur2007k}.
	Based on the information provided
	in table \ref{tbl_stroke_analysis}, only the five significant dimensions A, B, F, G, and H were utilized as sorting parameters.
	The number of clusters was determined empirically, using Mardia's rule of thumb \mbox{$k \approx \sqrt{n / 2}$} \cite{mardia2005multivariate}
	as an upper limit.

@@

	Initially, three simple routing strategies are being applied: a lookup table, a function that
	identifies the most similar centroid, and a feedforward neural network. One auxiliary goal
	at this stage---in particular with the ANN---is creating some degree of resilience to errors
	such as a missing or incorrectly traced strokes.
	A differing aspect at this stage compared to previous works is the vastly decreased number
	of input features being considered, e.g. 8 versus 256 in \cite{yang2003accelerating}.

@@

	Current efforts are focused on designing and evaluating convolutional neural networks to perform final, visual comparisons.
	\mbox{Convolutional} neural networks are known to provide a measure of resilience against translation and rotation,
	thus lending themselves well to offline character recognition tasks.

	The comparatively small number of category candidates per cluster (in current experiments averaging 128 kanji)
	implies that each model will require a lower degree of complexity. Furthermore, as it is probable that each
	partition will contain many similar-looking categories, it follows that the networks may be more likely to correctly
	discern between more minute differences that might have been generalized away in larger-scale topologies.
	These properties may lead to desireable reductions in execution time and storage space requirements,
	without considerable negative impact on recognition rates.

	%As previously stated, the comparatively small set of category candidates (in current experiments averaging 128 kanji)
	%implies that each cluster model requires a lower degree of complexity. It may also be expected that---seeing
	%how each partition is likely to contain many similar-looking characters---the networks will be more likely
	%to correctly discern between more minute differences that might have been generalized away in a larger-scale network.

	Finally, by focusing solely on offline character recognition at this stage, a significantly larger body of training data---such
	as the ETL character database, which contains hundreds of thousands of handwritten kanji samples \cite{yamamoto1986recognition}---may be utilized.

@@

	The experiments documented in this paper are an initial and ongoing attempt at implementing a kanji handwriting recognition \mbox{system}
	based on the outlined design methodology; numerous venues still remain to be explored.
